Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2014-11-15 tex/scam/supplement.tex
edits

Let $\pi_k(i)$ be an reordering of $X_k$ in ascending order so that $X_{k \pi_k(n)}$ is the largest entry. Let $\mathbf{1}_{\pi_k(i:n)}$ be 1 on the coordinates $\pi_k(i),\pi_k(i+1),...,\pi_k(n)$ and 0 elsewhere.

Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n \geq (X_{k\pi_k(n)} - X_{k\pi_k(1)})| \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$ and that $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{X_{k\pi_k(n)} - X_{k\pi_k(1)}} \geq \frac{1}{16}$.

Then the following are true:
\begin{enumerate}
\item Let $\hat{d}_k = 0$ for $k \in S^c$, then \{$\hat{d}_k\}_{k=1,...,p}$ is an optimal solution to optimization~\ref{opt:alternate_opt}. Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be zero and must be unique.
\end{enumerate}
\end{theorem}

@@

\begin{theorem} 
Suppose assumptions A1-A4 hold. Suppose $\sqrt{\log 2np} \geq 1$, and define $\tilde{\sigma} \equiv \max(\sigma, B)$. Suppose that $p \leq O\exp( c'' n)$ for some $c'' > 0$ and that $n \geq C''$ for some constant $C''$ possibly dependent on $b$.

If $\lambda_n \geq (8 \cdot 32) 2 b s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{24}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
\begin{align*}
& \lambda_n > (X_{k\pi_k(n)} - X_{k\pi_k(1)}) \Big| \frac{32}{n}\hat{r}^\tran \mathbf{1}_{\pi_k(i':n)} \Big|  
\end{align*}
and for all $k \in S^c$ and $i' = 1, ..., n-1$, $\frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{X_{k\pi_k(n)} - X_{k\pi_k(1)}} \leq \frac{1}{16}$.

@@

Finally, we note that $2b \geq (X_{k\pi_k(n)} - X_{k\pi_k(1)})$ by definition. This concludes the proof for the first part of the theorem.

To prove the second claim, let the interval $[-b, b]$ be divided into $64$ non-overlapping segments each of length $b/32$. Because $X_k$ is drawn from a continuous density, the density has a lower bound $c_l > 0$ and the probability that every segment contains some samples $X_{ki}$'s is at least $1-64 \left( 1 - \frac{b}{32} c_l \right)^n$. Let $\mathcal{E}_k$ denote the event that every segment contains some samples.

Define $\mathsf{gap}_i = X_{k \pi_k(i+1)} - X_{k \pi_k(i)}$ where $\mathsf{gap}_0 = X_{k \pi_k(1)} - (-b)$ and $\mathsf{gap}_{n} = b - X_{k\pi_k(n)}$.

If any $\mathsf{gap}_i \geq \frac{b}{16}$, then $\mathsf{gap}_i$ has to contain one of the segments. Therefore, under event $\mathcal{E}_k$, it must be that $\mathsf{gap}_i \leq \frac{b}{16}$ for all $i$.

Thus, we have that, for all $i$:

\[
\frac{X_{k\pi_k(i+1)} - X_{k \pi_k(i)}}{X_{k\pi_k(n)} - X_{k \pi_k(1)}} \geq 
\frac{ b/16 }{ 2b - b/8} \geq 1/16
\]

Taking an union bound for each $k \in S^c$, the probability of that all $\mathcal{E}_k$ hold is at least $1 - p 64 \left( 1 - \frac{b}{32} c_l \right)^n$.

$64 \left( 1 - \frac{b}{32} c_l \right)^n = C' p \exp( - c' n)$ for some positive constants $c', C'$ dependent on $b, c_l$. Therefore, if $p \leq exp( c'' n)$ for some $c'' < c'$ and if $n$ is large enough, $C' p \exp( - c' n) \leq C' \exp( - (c' - c'') n) \leq \frac{12}{n}$.

@@

Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-b,b]$. Let $\mathcal{C}^1_B \equiv \{ f \in \mathcal{C}^1 \,:\, \| f \|_\infty \leq B \}$ denote the set of $B$-bounded univariate convex functions. 
Define $\mathcal{C}^s$ as the set of convex additive functions and
$\mathcal{C}^s_B$ likewise as the set of convex additive functions
whose components are $B$-bounded:
\begin{align*}
\mathcal{C}^s &\equiv \{ f \,:\, f = \sum_{k=1}^s f_k, \,
   f_k \in \mathcal{C}^1 \} \\
\mathcal{C}^s_B &\equiv \{ f \in \mathcal{C}^s \,:\, 
f = \sum_{k=1}^s f_k, \, \| f_k \|_\infty \leq B \}.
\end{align*}
Let $f^*(x) = \sum_{k=1}^s f^*_k(x_k)$ be the population risk minimizer:
\[
f^* = \arg\min_{f \in \mathcal{C}^s} \| f_0 - f^* \|_P^2
\]
We let $sB$ be an upper bound on $\| f_0 \|_\infty$ and $B$ be an
upper bound on $\| f^*_k \|_\infty$. 
It follows that $\|f^* \|_\infty \leq s B$.

@@

\begin{theorem}
\label{thm:convex_consistent}
Let $\tilde{\sigma} \equiv \max(\sigma, B)$, and let $\hat{f}$ be the
minimizer of the restricted regression with $\lambda \leq 9 s
\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
Suppose $n \geq c_1 s \sqrt{sB}$.
Then with probability at least $1-\frac{C}{n}$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np},
\end{align}
where $c_1$ is an absolute constant and $c, C$ are constants possibly dependent on $b$.
\end{theorem}

@@

Define $\mathcal{G} =\{ f - f^* + \bar{f}^* \,:\, f \in
\mathcal{C}^s_B \}$ 
as the set of convex additive functions centered around the function $f^* - \bar{f}^*$. 
By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose size is bounded by $\log N_{[]}( 2\epsilon, \mathcal{G}, L_1(P)) \leq sK^{**} \left( \frac{2sbB}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3]$.
Let us suppose condition~\ref{cond:simplify_covering_number} holds. Then, by Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h_U, h_L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$, 
$\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sbB
)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. We verify at the
end of the proof that 
condition~\ref{cond:simplify_covering_number} indeed holds.

For each $h \in \mathcal{G}$, there exists a pair $(h_U, h_L)$ such that $h_U(X_i) - h_L(X_i) \geq h(X_i) - h_L(X_i) \geq 0$. Therefore, with probability at least $1-\delta$, uniformly for all $h \in \mathcal{G}$:
$$
\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}.
$$
We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{
  \frac{sK^{**}(2sbB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2}
    n}}$. Let $\mathcal{E}_{[\,]}$ denote the event that for each $h
\in \mathcal{G}$, there exists $h_L$ in the $\epsilon$-bracketing such
that $\|h-h_L\|_{L_{P_n}} \leq 2\epsilon + \epsilon_{n, \delta}$. Then
$\mathcal{E}_{[\,]}$ has probability at most $1-\delta$ as shown.

@@

Putting this together, we have that
\begin{align*}
\lefteqn{|\langle w, h \rangle_n | \leq | \langle w, h_L\rangle_n| + |\langle w, h - h_L\rangle_n|}\\
\lefteqn{|\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| \leq 
     | \sup_{h^L} \langle w, h_L \rangle_n | + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, 2\delta})} \\
   &\leq   sB \sigma \sqrt{ 2 \frac{ \log N_{[]} + \log \frac{1}{\delta}}{n}} + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
   &\leq  sB \sigma \sqrt{ 2 \frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
   \sigma \sqrt{ 2\log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
   &\leq sB \sigma \sqrt{ 2\frac{sK^{**} (2sbB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
   2\sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sbB)^{1/2}\log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
   &\leq 2\sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sbB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}}.
\end{align*}
To balance the two terms, we set $\epsilon = sB \sqrt{ \frac{(s
    K^{**} (sBb)^{1/2})^{4/5}}{n^{4/5}} }$. It is easy to verify that
if $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$, then 
$\epsilon \in (0, sB \epsilon_3]$ for some absolute constant $\epsilon_3$ as required by the bracketing number results (Corollary~\ref{cor:convexadditive_lp}). Furthermore, conditions~\eqref{cond:simplify_covering_number} also hold.

In summary, we have that probability at least $1-\delta$,
\[
|\sup_{h \in \mathcal{G}} \langle w, h \rangle | \leq c sB \sigma \sqrt{ 
   \frac{s^{6/5} B^{2/5} \log^2 \frac{Cn}{\delta}}{n^{4/5}}} \leq 
  c sB \sigma \sqrt{ 
   \frac{s (sB)^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
\]
where we absorbed $b, K^{**}$ into the constant $c$ and the union bound multipliers into the constant $C$.
% Then, $\| h \|_n \leq \| h \|_\infty \leq 4sLb$ for all $h \in \mathcal{G}$.\\
% According to theorem~\ref{thm:chaining}, for all $\epsilon > \frac{1}{\sqrt{n}}\sigma c \int_0^R \sqrt{ \log N_2(t, \mathcal{G}) }dt \vee R$,
% \[
% P\Big( \sup_{h \in \mathcal{G}} \langle w, h \rangle_n \geq \epsilon \Big) \leq
%   4 \exp \Big( - \frac{ n \epsilon^2}{ c R^2 \sigma^2} \Big)
% \]
% where $R = 4sLb$ for our purpose.

@@

\textbf{Step 3.} Continuing from
equation~\eqref{eqn:second_step_inequality}, we use
Lemma~\ref{lem:uniform_convergence} and another union bound to obtain
that, with probability at least $1-3\delta$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
   &\leq cB^2 \sigma 
    \sqrt{ \frac{s^4}{n^{4/5}} \log^2 \frac{Cn}{\delta}}
 +\lambda 2 s B + c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
    \nonumber \\
&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB \nonumber
\end{align}
Substituting in $\lambda \leq 9 s \tilde{\sigma} \sqrt{\frac{1}{n}
  \log^2 np}$ and $\delta = \frac{C}{n}$ we obtain the statement of
the theorem.
\end{proof}

@@

\begin{theorem}
\label{thm:concave_consistent}
Let $\hat{g}_k$ denote the minimizer of the concave postprocessing
step with $\lambda_n \leq 9 s\tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq c_1 B^4 \tilde{\sigma}^2 s^5$ where $c_1 \geq 1$ is an absolute constant.
Then with probability at least $1- \frac{C}{n}$, for all $k=1,...,s$,
\[
\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \tilde{\sigma}^{1/2} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 np}.
\]
\end{theorem}

@@

\textbf{Step 1.} To bound term 1, we start from the definition of
$\hat{g}_k$ and obtain
\begin{align*}
\| y - \hat{f} - \hat{g}_k \|_n^2 + \lambda_n \| \hat{g} \|_\infty &\leq
   \| y - \hat{f} - g^*_k \|_n^2 + \lambda_n \| g^* \|_\infty \\
\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - g^*_k \|_n^2 + \lambda_n 2B \\[10pt]
\| f_0 - \hat{f} - \hat{g}_k + w\|_n^2 & \leq \| f_0 - \hat{f} - g^*_k + w \|_n^2 
   +\lambda_n 2 B \\
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 -\hat{f} - g^*_k\|_n^2 &\leq
   2 \langle w, \hat{g}_k - g^*_k \rangle_n + \lambda_n 2B.
\end{align*}
Using the same bracketing analysis as in Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
  c B^2 \sigma \sqrt{ \frac{b^{1/2}}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda_n 2 B.
\end{align*}
The condition $n \geq c_1 s\sqrt{sB}$ in the proof of Theorem~\ref{thm:convex_consistent} is satisfied here because we assume that $n^{4/5} \geq c_1 B^4 \tilde{\sigma}^2 s^5 \log^2 np$ in the statement of the theorem.
We now integrate terms involving only $b$ into the constant $c$. Using the uniform convergence result of Lemma~\ref{lem:uniform_convergence}, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
  c B^2 \sigma \sqrt{ \frac{1}{n} \log \frac{Cn}{\delta} }+ \lambda_n 2 B +
  c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
 &\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^5}{n^{4/5}} \log \frac{C}{\delta}}+ \lambda_n 2B
\end{align*}

@@

subsubsection{Concentration of Measure}

>>>>

Let $\pi_k(i)$ be an reordering of $X_k$ in ascending order so that $X_{k \pi_k(n)}$ is the largest entry. Let $\mathbf{1}_{\pi_k(i:n)}$ be 1 on the coordinates $\pi_k(i),\pi_k(i+1),...,\pi_k(n)$ and 0 elsewhere. Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k \pi_k(1)}$.

Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n \geq \mathsf{range}_k | \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$, and $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{\mathsf{range}_k} \geq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.

Then the following are true:
\begin{enumerate}
\item Let $\hat{d}_k = 0$ for $k \in S^c$, then \{$\hat{d}_k\}_{k=1,...,p}$ is an optimal solution to optimization~\ref{opt:alternate_opt}. Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be zero and unique.
\end{enumerate}
\end{theorem}

@@

\begin{theorem} 
Suppose assumptions A1-A5 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$. Suppose that $p \leq O\big( \exp( c n) \big)$ and $n \geq C$ for some constants $c,C$. Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k\pi_k(1)}$.

If $\lambda_n \geq 2 (8 \cdot 32) s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{24}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
\begin{align*}
& \lambda_n > \mathsf{range}_k \Big| \frac{32}{n}\hat{r}^\tran \mathbf{1}_{\pi_k(i':n)} \Big|  
\end{align*}
and $\max_{i'} \frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{\mathsf{range}_k} \leq \frac{1}{16}$ and $\mathsf{range}_k \geq 1$.

@@

Finally, we note that $2 \geq (X_{k\pi_k(n)} - X_{k\pi_k(1)})$ since $X_k \subset [-1,1]$. This concludes the proof for the first part of the theorem.

To prove the second and third claim, let the interval $[-1, 1]$ be divided into $64$ non-overlapping segments each of length $1/32$. Because $X_k$ is drawn from a density with a lower bound $c_l > 0$, the probability that every segment contains some samples $X_{ki}$'s is at least $1-64 \left( 1 - \frac{1}{32} c_l \right)^n$. Let $\mathcal{E}_k$ denote the event that every segment contains some samples.

Define $\mathsf{gap}_i = X_{k \pi_k(i+1)} - X_{k \pi_k(i)}$ for $i=1,...,n-1$ and define $\mathsf{gap}_0 = X_{k \pi_k(1)} - (-1)$ and $\mathsf{gap}_{n} = 1 - X_{k\pi_k(n)}$.

If any $\mathsf{gap}_i \geq \frac{1}{16}$, then $\mathsf{gap}_i$ has to contain one of the segments. Therefore, under event $\mathcal{E}_k$, it must be that $\mathsf{gap}_i \leq \frac{1}{16}$ for all $i$.

Thus, we have that $\mathsf{range}_k \geq 2 - 1/8 \geq 1$ and that for all $i$:

\[
\frac{X_{k\pi_k(i+1)} - X_{k \pi_k(i)}}{\mathsf{range}_k} \geq 
\frac{ 1/16 }{ 2 - 1/8} \geq 1/16
\]

Taking an union bound for each $k \in S^c$, the probability of that all $\mathcal{E}_k$ hold is at least $1 - p 64 \left( 1 - \frac{1}{32} c_l \right)^n$.

$64 \left( 1 - \frac{1}{32} c_l \right)^n = C' p \exp( - c' n)$ for some positive constants $c', C'$ dependent on $c_l$. Therefore, if $p \leq exp( c'' n)$ for some $c'' < c'$ and if $n$ is large enough, $C' p \exp( - c' n) \leq C' \exp( - (c' - c'') n) \leq \frac{12}{n}$.

@@

Let $\mathcal{C}^1$ denote the set of univariate convex functions supported on $[-1,1]$. Let $\mathcal{C}^1_B \equiv \{ f \in \mathcal{C}^1 \,:\, \| f \|_\infty \leq B \}$ denote the set of $B$-bounded univariate convex functions. 
Define $\mathcal{C}^s$ as the set of convex additive functions and
$\mathcal{C}^s_B$ likewise as the set of convex additive functions
whose components are $B$-bounded:
\begin{align*}
\mathcal{C}^s &\equiv \{ f \,:\, f = \sum_{k=1}^s f_k, \,
   f_k \in \mathcal{C}^1 \} \\
\mathcal{C}^s_B &\equiv \{ f \in \mathcal{C}^s \,:\, 
f = \sum_{k=1}^s f_k, \, \| f_k \|_\infty \leq B \}.
\end{align*}
Let $f^*(x) = \sum_{k=1}^s f^*_k(x_k)$ be the population risk minimizer:
\[
f^* = \arg\min_{f \in \mathcal{C}^s} \| f_0 - f^* \|_P^2
\]
We let $sB$ be an upper bound on $\| f_0 \|_\infty$ and $B$ be an
upper bound on $\| f^*_k \|_\infty$. 
It follows that $\|f^* \|_\infty \leq s B$.

@@

\begin{theorem}
\label{thm:convex_consistent}
Let $\tilde{\sigma} \equiv \max(\sigma, B)$, and let $\hat{f}$ be the
minimizer of the restricted regression with $\lambda \leq 512 s
\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
Suppose $n \geq c_1 s \sqrt{sB}$.
Then with probability at least $1-\frac{C}{n}$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np},
\end{align}
where $c_1$ is an absolute constant and $c, C$ are constants possibly dependent on $b$.
\end{theorem}

@@

Define $\mathcal{G} =\{ f - f^* + \bar{f}^* \,:\, f \in
\mathcal{C}^s_B \}$ 
as the set of convex additive functions centered around the function $f^* - \bar{f}^*$. 
By Corollary~\ref{prop:convexbracket_lp}, there is an $\epsilon$-bracketing of $\mathcal{G}$ whose size is bounded by $\log N_{[]}( 2\epsilon, \mathcal{G}, L_1(P)) \leq sK^{**} \left( \frac{2sB}{\epsilon} \right)^{1/2}$, for all $\epsilon \in (0, sB \epsilon_3]$.
Let us suppose condition~\ref{cond:simplify_covering_number} holds. Then, by Corollary~\ref{cor:convexbracket_ln}, with probability at least $1-\delta$, each bracketing pair $(h_U, h_L)$ is close in $L_1(P_n)$ norm, i.e., for all $(h_U, h_L)$, 
$\frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i) | \leq 2 \epsilon + sB \sqrt{ \frac{sK^{**}(2sB
)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}$. We verify at the
end of the proof that 
condition~\ref{cond:simplify_covering_number} indeed holds.

For each $h \in \mathcal{G}$, there exists a pair $(h_U, h_L)$ such that $h_U(X_i) - h_L(X_i) \geq h(X_i) - h_L(X_i) \geq 0$. Therefore, with probability at least $1-\delta$, uniformly for all $h \in \mathcal{G}$:
$$
\frac{1}{n} \sum_{i=1}^n |h(X_i) - h_L(X_i)| \leq \frac{1}{n} \sum_{i=1}^n | h_U(X_i) - h_L(X_i)| \leq 2\epsilon +  (sB) \sqrt{ \frac{sK^{**}(2sB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2} n}}.
$$
We denote $\epsilon_{n,\delta} \equiv (sB) \sqrt{
  \frac{sK^{**}(2sB)^{1/2} \log \frac{1}{\delta}}{2\epsilon^{1/2}
    n}}$. Let $\mathcal{E}_{[\,]}$ denote the event that for each $h
\in \mathcal{G}$, there exists $h_L$ in the $\epsilon$-bracketing such
that $\|h-h_L\|_{L_{P_n}} \leq 2\epsilon + \epsilon_{n, \delta}$. Then
$\mathcal{E}_{[\,]}$ has probability at most $1-\delta$ as shown.

@@

Putting this together, we have that
\begin{align*}
\lefteqn{|\langle w, h \rangle_n | \leq | \langle w, h_L\rangle_n| + |\langle w, h - h_L\rangle_n|}\\
\lefteqn{|\sup_{h \in \mathcal{G}} \langle w, h \rangle_n| \leq 
     | \sup_{h^L} \langle w, h_L \rangle_n | + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, 2\delta})} \\
   &\leq   sB \sigma \sqrt{ 2 \frac{ \log N_{[]} + \log \frac{1}{\delta}}{n}} + \sigma \sqrt{2 \log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
   &\leq  sB \sigma \sqrt{ 2 \frac{sK^{**} (2sB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
   \sigma \sqrt{ 2\log \frac{2n}{\delta}} (2\epsilon + \epsilon_{n, \delta}) \\
   &\leq sB \sigma \sqrt{ 2\frac{sK^{**} (2sB)^{1/2} \log \frac{1}{\delta}}{n \epsilon^{1/2}}} +
   2\sigma\sqrt{2 \log \frac{2n}{\delta}} \epsilon + sB \sigma \sqrt{2 \frac{sK^{**} (2sB)^{1/2}\log \frac{1}{\delta}}{n \epsilon^{1/2}} \log \frac{2n}{\delta}} \\
   &\leq 2\sigma\sqrt{2\log \frac{2n}{\delta}} \epsilon + 2 sB \sigma \sqrt{ \frac{sK^{**} (2sB)^{1/2} \log^2 \frac{2n}{\delta}}{n \epsilon^{1/2}}}.
\end{align*}
To balance the two terms, we set $\epsilon = sB \sqrt{ \frac{(s
    K^{**} (sB)^{1/2})^{4/5}}{n^{4/5}} }$. It is easy to verify that
if $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$, then 
$\epsilon \in (0, sB \epsilon_3]$ for some absolute constant $\epsilon_3$ as required by the bracketing number results (Corollary~\ref{cor:convexadditive_lp}). Furthermore, conditions~\eqref{cond:simplify_covering_number} also hold.

In summary, we have that probability at least $1-\delta$,
\[
|\sup_{h \in \mathcal{G}} \langle w, h \rangle | \leq c sB \sigma \sqrt{ 
   \frac{s^{6/5} B^{2/5} \log^2 \frac{Cn}{\delta}}{n^{4/5}}} \leq 
  c sB \sigma \sqrt{ 
   \frac{s (sB)^{1/2} \log^2 \frac{Cn}{\delta}}{n^{4/5}}}
\]
where we absorbed $K^{**}$ into the constant $c$ and the union bound multipliers into the constant $C$.
% Then, $\| h \|_n \leq \| h \|_\infty \leq 4sLb$ for all $h \in \mathcal{G}$.\\
% According to theorem~\ref{thm:chaining}, for all $\epsilon > \frac{1}{\sqrt{n}}\sigma c \int_0^R \sqrt{ \log N_2(t, \mathcal{G}) }dt \vee R$,
% \[
% P\Big( \sup_{h \in \mathcal{G}} \langle w, h \rangle_n \geq \epsilon \Big) \leq
%   4 \exp \Big( - \frac{ n \epsilon^2}{ c R^2 \sigma^2} \Big)
% \]
% where $R = 4sLb$ for our purpose.

@@

\textbf{Step 3.} Continuing from
equation~\eqref{eqn:second_step_inequality}, we use
Lemma~\ref{lem:uniform_convergence} and another union bound to obtain
that, with probability at least $1-3\delta$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
   &\leq cB^2 \sigma 
    \sqrt{ \frac{s^4}{n^{4/5}} \log^2 \frac{Cn}{\delta}}
 +\lambda 2 s B + c B^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
    \nonumber \\
&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{Cn}{\delta}} + \lambda 2 sB \nonumber
\end{align}
Substituting in $\lambda \leq 512 s \tilde{\sigma} \sqrt{\frac{1}{n}
  \log^2 np}$ and $\delta = \frac{C}{n}$ we obtain the statement of
the theorem.
\end{proof}

@@

\begin{theorem}
\label{thm:concave_consistent}
Let $\hat{g}_k$ denote the minimizer of the concave postprocessing
step with $\lambda_n \leq 512 s\tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq c' B^4 \tilde{\sigma}^2 s^5$ where $c' \geq 1$ is a constant.
Then with probability at least $1- \frac{C}{n}$, for all $k=1,...,s$,
\[
\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \tilde{\sigma}^{1/2} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 np}.
\]
\end{theorem}

@@

\textbf{Step 1.} To bound term 1, we start from the definition of
$\hat{g}_k$ and obtain
\begin{align*}
\| y - \hat{f} - \hat{g}_k \|_n^2 + \lambda_n \| \hat{g} \|_\infty &\leq
   \| y - \hat{f} - g^*_k \|_n^2 + \lambda_n \| g^* \|_\infty \\
\| y - \hat{f} - \hat{g}_k \|_n^2 &\leq \| y - \hat{f} - g^*_k \|_n^2 + \lambda_n 2B \\[10pt]
\| f_0 - \hat{f} - \hat{g}_k + w\|_n^2 & \leq \| f_0 - \hat{f} - g^*_k + w \|_n^2 
   +\lambda_n 2 B \\
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 -\hat{f} - g^*_k\|_n^2 &\leq
   2 \langle w, \hat{g}_k - g^*_k \rangle_n + \lambda_n 2B.
\end{align*}
Using the same bracketing analysis as in Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
  c B^2 \sigma \sqrt{ \frac{1}{n^{4/5}} \log \frac{C}{\delta} }+ \lambda_n 2 B.
\end{align*}
The condition $n \geq c_1 s\sqrt{sB}$ in the proof of Theorem~\ref{thm:convex_consistent} is satisfied here because we assume that $n^{4/5} \geq c_1 B^4 \tilde{\sigma}^2 s^5 \log^2 np$ in the statement of the theorem.
Using the uniform convergence result of Lemma~\ref{lem:uniform_convergence}, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
  c B^2 \sigma \sqrt{ \frac{1}{n} \log \frac{Cn}{\delta} }+ \lambda_n 2 B +
  c B^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
 &\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^5}{n^{4/5}} \log \frac{C}{\delta}}+ \lambda_n 2B
\end{align*}

@@

\begin{lemma}
\label{lem:additive_uniqueness}
Let $p(\mathbf{x})$ be a positive density over $[0,1]^p$. Let $\phi(\mathbf{x}) = \sum_{j=1}^p \phi_j(x_j)$ be an additive function.

Suppose that for all $j$, $\phi_j(x_j)$ is bounded and $\E \phi_j(X_j) = 0$. Suppose for some $j$, $\E \phi_j(X_j)^2 > 0$, then it must be that $\E \phi(X)^2 > 0$. 
\end{lemma}

\begin{proof}

Suppose, for sake of contradiction, that

\begin{align*}
\E \phi(X)^2 = \E \left( \phi_j(X_j) + \phi_{-j} (X_{-j}) \right)^2 = 0.
\end{align*}

Let $A_+ = \{ x_j \,:\, \phi_j(x_j) \geq 0 \}$. Since $\E \phi_j(X_j) = 0$, $\E \phi_j(X_j)^2 > 0$, and $\phi_j$ is bounded, it must be that both $A_+$ has probability greater than 0.

Now, define $B_+ = \{ x_{-j} \,:\, \phi_{-j}(x_{-j}) \geq 0 \}$. $B_+$ then must have probability greater than 0 as well.

Since $p(\mathbf{x})$ is a positive density, the set $A_+ \times B_+$ must have a positive probability. However, $\phi > 0$ on $A_+ \times B_+ \subset [0,1]^p$ which implies $\E \phi(X)^2 > 0$.

\subsubsection{Concentration of Measure}
